Does the COMPAS Needle Always Point Towards Equity? Finding Fairness in the COMPAS Risk Assessment Algorithm: A Case Study

### 2022-04-21 Paper_Draft2/Draft2.Rmd
updating author section again

author:
  - name: Amrita Acharya
    affil: 1
  - name: Dianne Caravela
    affil: 1
  - name: Eunice Kim
    affil: 1
  - name: Emma Kornberg
    affil: 1
  - name: Elisabeth Nesmith
    affil: 1
affiliation:
  - num: 1
    address: |
      Statistical and Data Sciences
      Smith College
      Northampton, MA 01063
    email: aacharya@smith.edu, dcaravela@smith.edu, ekim89@smith.edu, ekornberg@smith.edu, enesmith@smith.edu

journal: water
type: article
status: submit
bibliography: mybibfile.bib
csl: ../resources/chicago-author-date.csl
#appendix: appendix.tex
classoption: fleqn
correspondence: |
  bbaumer@smith.edu

>>>>

author:
  - name: Amrita Acharya
    affil: 1
  - name: Dianne Caravela
    affil: 1
  - name: Eunice Kim
    affil: 1
  - name: Emma Kornberg
    affil: 1
  - name: Elisabeth Nesmith
    affil: 1
affiliation:
  - num: 1
    address: |
      Statistical and Data Sciences
      Smith College
      Northampton, MA 01063
    email: bbaumer@smith.edu

journal: water
type: article
status: submit
bibliography: mybibfile.bib
csl: ../resources/chicago-author-date.csl
#appendix: appendix.tex
classoption: fleqn
correspondence: |
  aacharya@smith.edu, dcaravela@smith.edu, ekim89@smith.edu, ekornberg@smith.edu, enesmith@smith.edu

### 2022-04-21 Paper_Draft2/Draft2.tex
updating author section again

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Statistical and Data Sciences Smith College Northampton, MA
01063; \href{mailto:aacharya@smith.edu}{\nolinkurl{aacharya@smith.edu}},
\href{mailto:dcaravela@smith.edu}{\nolinkurl{dcaravela@smith.edu}},
\href{mailto:ekim89@smith.edu}{\nolinkurl{ekim89@smith.edu}},
\href{mailto:ekornberg@smith.edu}{\nolinkurl{ekornberg@smith.edu}},
\href{mailto:enesmith@smith.edu}{\nolinkurl{enesmith@smith.edu}}\\
}
% Contact information of the corresponding author
\corres{Correspondence: \href{mailto:bbaumer@smith.edu}{\nolinkurl{bbaumer@smith.edu}}}

>>>>

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Statistical and Data Sciences Smith College Northampton, MA
01063; \href{mailto:bbaumer@smith.edu}{\nolinkurl{bbaumer@smith.edu}}\\
}
% Contact information of the corresponding author
\corres{Correspondence: \href{mailto:aacharya@smith.edu}{\nolinkurl{aacharya@smith.edu}},
\href{mailto:dcaravela@smith.edu}{\nolinkurl{dcaravela@smith.edu}},
\href{mailto:ekim89@smith.edu}{\nolinkurl{ekim89@smith.edu}},
\href{mailto:ekornberg@smith.edu}{\nolinkurl{ekornberg@smith.edu}},
\href{mailto:enesmith@smith.edu}{\nolinkurl{enesmith@smith.edu}}}
